### 2013-03-23 doc/sosp13/abstract.tex
minor edits

Grappa serves both as a C++ user library and as a foundation upon which higher
level languages can be developed or adapted. Grappa tolerates delays to remote
memory by multiplexing thousands of lightweight tasks to each processor core;
balances load via fine-grained distributed work-stealing; takes full advantage
of network characteristics by aggregating smaller data requests into large
ones; and provides efficient synchronization and remote operations. We present
a detailed description of the Grappa system, programming examples using the
library interface, and compare performance for several irregular benchmarks to
hand-optimized MPI code and the Cray XMT, a custom system used to target the
real time graph analytics market.

>>>>

Grappa serves both as a C++ user library and as a foundation upon which higher
level languages can be developed or adapted. Grappa tolerates delays to remote
memory by multiplexing thousands of lightweight execution contexts to each
processor core; balances load via fine-grained distributed work-stealing;
takes full advantage of network characteristics by aggregating smaller data
requests into large ones; and provides efficient synchronization and remote
operations. We present a detailed description of the Grappa system,
programming examples using the library interface, and compare performance for
several irregular benchmarks to hand-optimized MPI code and the Cray XMT, a
custom system used to target the real time graph analytics market.
